---
output:
  pdf_document: default
  html_document: default
---

---
title: "Brain activity foreshadows stock price dynamics"
output:
  html_notebook: default
  html_document: default


## Load libraries
```{r, include=F}
library(reshape2)
library(dplyr)
library(ggplot2)
library(lmerTest)
require(MuMIn)
source('../rsquaredglmm.R') 
source('../Functions.R')
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#D55E00", "#F0E442", "#0072B2", "#CC79A7", "#999999")

# Read df with data per stock for forecasting analyses
gdf <- read.csv('../../voi_csv/data.csv')
```

#Experiment 1
```{r}
# Choice model (Behavioral model)
ans <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ Choice"), type='glm', split.method ='average', days_train=9)
print(ans)

# Market model
ans <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ slope + volatility + Previous_Trial"), type='glm', split.method ='average', days_train=9)

# Neural model 
ans <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4"), type='glm', split.method ='average', days_train=9)
print(ans) 

# Combined model
ans <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', days_train=9)
print(ans) 

# Compare models Experiment 1
model_Choice <- glm("Result ~ Choice", data = filter(gdf, Experiment==1), family = binomial(link = logit))

model_Market <- glm("Result ~ slope + volatility + Previous_Trial", data = filter(gdf, Experiment==1), family = binomial(link = logit))

model_Neural <- glm("Result ~ nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4", data = filter(gdf, Experiment==1), family = binomial(link = logit))

model_Combined <- glm("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility", data = filter(gdf, Experiment==1), family = binomial(link = logit))

lrtest(model_Market, model_Combined)
anova(model_Market, model_Combined, test = "LRT")

lrtest(model_Choice, model_Combined)
anova(model_Choice, model_Combined, test = "LRT")

lrtest(model_Neural, model_Combined)
anova(model_Neural, model_Combined, test = "LRT")
```

# Experiment 2
```{r}
# Choice model (Behavioral model)
ans <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ Choice"), type='glm', split.method ='average', days_train=9)
print(ans)

# Market model
ans <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ slope + volatility + Previous_Trial"), type='glm', split.method ='average', days_train=9)

# Neural model
ans <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4"), type='glm', split.method ='average', days_train=9)
print(ans) 

# Combined model
ans <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', days_train=9)
print(ans) 

# Compare models Experiment 2
model_Choice <- glm("Result ~ Choice", data = filter(gdf, Experiment==2), family = binomial(link = logit))

model_Market <- glm("Result ~ slope + volatility + Previous_Trial", data = filter(gdf, Experiment==2), family = binomial(link = logit))

model_Neural <- glm("Result ~ nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4", data = filter(gdf, Experiment==2), family = binomial(link = logit))

model_Combined <- glm("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility", data = filter(gdf, Experiment==2), family = binomial(link = logit))

lrtest(model_Market, model_Combined)
anova(model_Market, model_Combined, test = "LRT")

lrtest(model_Choice, model_Combined)
anova(model_Choice, model_Combined, test = "LRT")

lrtest(model_Neural, model_Combined)
anova(model_Neural, model_Combined, test = "LRT")
```

# Reduced model with only AIns * Previous_Trial 
```{r}
summary(glm('Result ~ desai_insb_TR_4*Previous_Trial', data = filter(gdf, Experiment==1), family = binomial(link = logit)))

summary(glm('Result ~ desai_insb_TR_4*Previous_Trial', data = filter(gdf, Experiment==2), family = binomial(link = logit)))
```

# Interaction AIns*Previous_Trial; Post-hoc T-tests, Exp 1 and Exp 2
```{r}
# Post-hoc t-tests to compare AIns activity in inflection vs no inflection trials
gdf_E1_inflection <- filter(gdf, (Experiment =='1' & Is_Inflection == 1))
gdf_E1_noinflection <- filter(gdf, (Experiment =='1' & Is_Inflection == 0))

gdf_E2_inflection <- filter(gdf, (Experiment =='2' & Is_Inflection == 1))
gdf_E2_noinflection <- filter(gdf, (Experiment =='2' & Is_Inflection == 0))

t.test(gdf_E1_inflection$desai_insb_TR_4, gdf_E1_noinflection$desai_insb_TR_4, paired=F)
t.test(gdf_E2_inflection$desai_insb_TR_4, gdf_E2_noinflection$desai_insb_TR_4, paired=F)

sd(gdf_E1_inflection$desai_insb_TR_4)
sd(gdf_E1_noinflection$desai_insb_TR_4)
sd(gdf_E2_inflection$desai_insb_TR_4)
sd(gdf_E2_noinflection$desai_insb_TR_4)

# Post-hoc t-tests for AIns activation for Result - Goes Down after previous Up or Down day
# Exp1
gdf_E1 <- filter(gdf, Experiment =='1')
up_rd <- filter(gdf_E1, (Result=='Result - Goes Down' & Previous_Trial=="Went Up"))
down_rd <- filter(gdf_E1, (Result=='Result - Goes Down' & Previous_Trial=="Went Down"))
sd(up_rd$desai_insb_TR_4)
sd(down_rd$desai_insb_TR_4)

t.test(up_rd$desai_insb_TR_4, down_rd$desai_insb_TR_4, paired=F)

# Exp2
gdf_E2 <- filter(gdf, Experiment =='2')
up_rd <- filter(gdf_E2, (Result=='Result - Goes Down' & Previous_Trial=="Went Up"))
down_rd <- filter(gdf_E2, (Result=='Result - Goes Down' & Previous_Trial=="Went Down"))
sd(up_rd$desai_insb_TR_4)
sd(down_rd$desai_insb_TR_4)

t.test(up_rd$desai_insb_TR_4, down_rd$desai_insb_TR_4, paired=F)
```

# Classification analyses: Forecasting stock prices out of sample
```{r}
# Specify downsample.var in order for results to be downsampled (e.g. downsample.var = 'Result')

# Train on Combined model of Experiment 1 and test on data of Experiment 2
set.seed(0)
ans1 <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', downsample.var = 'Result', split.method ='average', d.test=filter(gdf, Experiment==2))
kable(ans1)

# Train on Combined model of Experiment 2 and test on data of Experiment 1
set.seed(0)
ans2 <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', downsample.var = 'Result', d.test=filter(gdf, Experiment==1))
kable(ans2)

# Train on reduced model with interaction between AIns and PreviousTrial in Experiment 1 [2] and test on data of Experiment 2 [1]
set.seed(0)
ans1 <- checkClassifier(filter(gdf, Experiment==1), as.formula("Result ~ desai_insb_TR_4*Previous_Trial"), type='glm', split.method ='average', downsample.var = 'Result', d.test=filter(gdf, Experiment==2))
kable(ans1)

set.seed(0)
ans2 <- checkClassifier(filter(gdf, Experiment==2), as.formula("Result ~ desai_insb_TR_4*Previous_Trial"), type='glm', split.method ='average', downsample.var = 'Result', d.test=filter(gdf, Experiment==1))
kable(ans2)
```

# Forecasting stock prices using randomized stock data
```{r, error=F, warning=F, message=false}
# Combined model
gdf_rdm1 <- filter(gdf, Experiment ==1)
gdf_rdm2 <- filter(gdf, Experiment ==2)

NUM_ITERATIONS <- 500
results_train_1_test_2= t(matrix(NA, NUM_ITERATIONS, 9))
results_train_2_test_1= t(matrix(NA, NUM_ITERATIONS, 9))

set.seed(0)
for(i in 1: NUM_ITERATIONS){
  gdf_rdm1$Result <- sample(gdf_rdm1$Result, replace = F)
  gdf_rdm2$Result <- sample(gdf_rdm2$Result, replace = F)
  ans1 <- checkClassifier(gdf_rdm1, as.formula("Result  ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', d.test=filter(gdf, Experiment==2), complete_result=T, verbose=F)
  
  ans2 <- checkClassifier(gdf_rdm2, as.formula("Result  ~ Choice + (nacc8mmb_TR_4 + mpfcb_TR_4 + desai_insb_TR_4) *Previous_Trial + slope + volatility"), type='glm', split.method ='average', d.test=filter(gdf, Experiment==1), complete_result=T, verbose=F)
  
  results_train_1_test_2[, i] <- unlist(ans1)
  results_train_2_test_1[, i] <- unlist(ans2)
}
print("---------------------------------------------------")

train1.test2.result.df <- data.frame(t(results_train_1_test_2))
colnames(train1.test2.result.df) <- names(ans1)
print("Train 1 Test 2 Results")
meanResults12 <- colMeans(train1.test2.result.df)
print(meanResults12)
t.test(train1.test2.result.df$test_accuracy, mu=.5)

print("---------------------------------------------------")

train2.test1.result.df <- data.frame(t(results_train_2_test_1))
colnames(train2.test1.result.df) <- names(ans2)
print("Train 2 Test 1 Results")
meanResults21 <- colMeans(train2.test1.result.df)

print(meanResults21)
t.test(train2.test1.result.df$test_accuracy, mu=.5)

print("---------------------------------------------------")

# Reduced model: AIns interaction with Previous Trial
gdf_rdm1 <- filter(gdf, Experiment ==1)
gdf_rdm2 <- filter(gdf, Experiment ==2)

NUM_ITERATIONS <- 500
results_train_1_test_2= t(matrix(NA, NUM_ITERATIONS, 9))
results_train_2_test_1= t(matrix(NA, NUM_ITERATIONS, 9))

set.seed(0)
for(i in 1: NUM_ITERATIONS){
  gdf_rdm1$Result <- sample(gdf_rdm1$Result, replace = F)
  gdf_rdm2$Result <- sample(gdf_rdm2$Result, replace = F)
  ans1 <- checkClassifier(gdf_rdm1, as.formula("Result  ~  desai_insb_TR_4 *Previous_Trial"), type='glm', split.method ='average', d.test=filter(gdf, Experiment==2), complete_result=T, verbose=F)
  
  ans2 <- checkClassifier(gdf_rdm2, as.formula("Result  ~  desai_insb_TR_4 *Previous_Trial"), type='glm', split.method ='average', d.test=filter(gdf, Experiment==1), complete_result=T, verbose=F)
  
  results_train_1_test_2[, i] <- unlist(ans1)
  results_train_2_test_1[, i] <- unlist(ans2)
}
print("---------------------------------------------------")

train1.test2.result.df <- data.frame(t(results_train_1_test_2))
colnames(train1.test2.result.df) <- names(ans1)
print("Train 1 Test 2 Results")
meanResults12 <- colMeans(train1.test2.result.df)
print(meanResults12)
t.test(train1.test2.result.df$test_accuracy, mu=.5)

print("---------------------------------------------------")

train2.test1.result.df <- data.frame(t(results_train_2_test_1))
colnames(train2.test1.result.df) <- names(ans2)
print("Train 2 Test 1 Results")
meanResults21 <- colMeans(train2.test1.result.df)

print(meanResults21)
t.test(train2.test1.result.df$test_accuracy, mu=.5)

print("---------------------------------------------------")
```

